### 2015-01-28 paper.tex
added barrier rules

Constraint Grammar (CG) was first introduced by \cite{KarlssonTODO}. 
It a tool for disambiguating output by morphological analyser.

@@

\begin{lstlisting}
<the>     Det
<bear>    Noun, Sg
          Verb, Pl, Pres
          Verb, Inf
<sleep>   Noun, Pl
          Verb, Sg3, Pres
\end{lstlisting}

@@

\begin{lstlisting}
<the>     Det
<bear>    Noun, Sg
<sleep>   Verb, Sg3, Pres
\end{lstlisting}

CG can also be applied to shallow syntax. After having disambiguated
the text morphologically, we can apply possible syntactic labels. For
instance, a noun can have a syntactic role of subject, object or
predicative; and a verb in present tense 3rd person singular can be
only the main verb (possibly combined with a conjunction, e.g. ``the
bear eats and sleeps''). The next step is shown below; the analyses
chosen in the previous step are shown in the angle brackets, and
syntactic labels are fully capitalised and preceded by @.

\begin{lstlisting}
<the,  Det>                
<bear, N, Sg>           @SUBJ
                        @OBJ
                        @PREDC
<sleep, V, Sg3, Pres>   @MAINV
\end{lstlisting}

@@

\cite{koskenniemi92} include also clause boundaries (TODO read about
it), such as marking coordinated or subordinated clauses, or showing
beginning and end of an embedded clause.
%; so the parse would be complete if \emph{the} and \emph{bear} would belong to

@@

@@

Let us show this with a small example.
We have a set of variables describing properties of people: \texttt{is\_under\_18},
\texttt{has\_driving\_licence} and \texttt{is\_drunk}.

>>>>

Constraint Grammar (CG) was first introduced by \cite{KarlssonTODO}. 
It a tool for disambiguating output by morphological analyser.
CG can run on unrestricted text, given that the morphological analyser
has large vocabulary.

@@

\begin{lstlisting}
the     <Det>
bear    <Noun, Sg>
        <Verb, Pl, Pres>
        <Verb, Inf>
sleep   <Noun, Pl>
        <Verb, Sg3, Pres>
\end{lstlisting}

@@

\begin{lstlisting}
the     <Det>
bear    <Noun, Sg>
sleep   <Verb, Sg3, Pres>
\end{lstlisting}

\subsubsection{Syntax}

``Because syntax, just as morphological disambiguation, relies on
elimination of alternatives, it is advantageous to introduce all
simple syntactic instantiations at once. Readings not having syntactic
labels after morphological analysis get them via morphosyntactic
mapping.''

e.g. it makes sense
7: [Lem "they",Pron,Subj,Nom,P3]
if we have a morph tag, like a pron, to label it already
since we know that they can only be SUBJ
and them can only be OBJ

CG can also be applied to shallow syntax. After having disambiguated
the text morphologically, we can apply possible syntactic labels. For
instance, a noun can have a syntactic role of subject, object or
predicative; and a verb in present tense 3rd person singular can be
only the main verb (possibly combined with a conjunction, e.g. ``the
bear eats and sleeps''). The next step is shown below; the analyses
chosen in the previous step are shown in the angle brackets, and potential
syntactic labels are fully capitalised and preceded by @. The sign >
in the tag \texttt{@DN>} expresses head/modifier relation determiner of the next head nominal to the right

\begin{lstlisting}
the     <Det>            @DN>    
bear    <N, Sg>          @SUBJ
                         @OBJ
                         @PREDC
sleep   <V, Sg3, Pres>   @MAINV
\end{lstlisting}

@@

\cite{koskenniemi92} include also 4 types of clause boundaries (TODO read about
it), such as marking coordinated or subordinated clauses, or showing
beginning and end of an embedded clause.
%; so the parse would be complete if \emph{the} and \emph{bear} would belong to

@@

\begin{quote}The whole finite-state grammar consists of a set of rules which
constrain the possible choices of word Interpretations, tags and
boundaries to only those which are considered grammatical. The entire grammar Is effectively equivalent to the (theoretical) intersection of all individual rule automata. However, such an intersection would be impractical to compute due to Its huge size.
The logical task for any finite-state parser in the current approach is
to compute the intersection of the unanalyzed sentence automaton and
each rule automaton. Actual parsing can be done in several alternative
ways which are guaranteed to yield the same result, but which vary in
terms of efficiency.
\end{quote}

@@

Let us demonstrate this with a small example.
We have a set of variables describing properties of people: \texttt{is\_under\_18},
\texttt{has\_driving\_licence} and \texttt{is\_drunk}.
